Lies and the lying liars who tell them

### 2018-11-01 GSV-comment-brief.Rmd
make sure we pick up latest csv from home directory

---
title: "Lies and the lying liars who tell them"
subtitle: "Comment on Garbarino, Slonim and Villeval (2018)"
author: "David Hugh-Jones"
date: "`r Sys.Date()`"
header-includes:
  - \usepackage{setspace}
  - \usepackage{placeins}
  - \onehalfspacing
  - \usepackage{fontspec}
output:
  pdf_document:
    md_extensions: +raw_attribute
    latex_engine: xelatex
  tufte::tufte_handout:
    latex_engine: xelatex
    md_extensions: +raw_attribute
  bookdown::tufte_handout2:
    latex_engine: xelatex
    md_extensions: +raw_attribute
  bookdown::tufte_html2: 
    pandoc_args: ['--self-contained']
    keep_intermediates: true
bibliography: bibliography.bib
link-citations: yes
fontsize: 12pt
mainfont: Times New Roman
---

@@

if (rewrite_csv) {
  path <- paste0("GSV-sims", if (sample_from_pop) "-pop-sample", ".csv")

  readr::write_csv(sim_output, path = path)

@@

gsv_estimates <- suppressMessages(readr::read_csv(normalizePath("~/sim-outputOutput.csv")))

>>>>

---
title: "Lies and the lying liars who tell them"
subtitle: "Comment on Garbarino, Slonim and Villeval (2018)"
author: "David Hugh-Jones"
date: "`r Sys.Date()`"
header-includes:
  - \usepackage{setspace}
  - \usepackage{placeins}
  - \onehalfspacing
  - \usepackage{fontspec}
output:
  pdf_document:
    md_extensions: +raw_attribute
    latex_engine: xelatex
  tufte::tufte_handout:
    latex_engine: xelatex
    md_extensions: +raw_attribute
  bookdown::tufte_handout2:
    latex_engine: xelatex
    md_extensions: +raw_attribute
  bookdown::tufte_html2: 
    pandoc_args: ['--self-contained']
    keep_intermediates: true
bibliography: bibliography.bib
link-citations: yes
fontsize: 12pt
mainfont: Times New Roman
mathfont: Times New Roman
---

@@

  path_root <- paste0("GSV-sims", if (sample_from_pop) "-pop-sample")

if (rewrite_csv) {
  readr::write_csv(sim_output, path = paste0(path_root, ".csv"))

@@

output_path <- paste0(path_root, "Output.csv")
gsv_estimates <- suppressMessages(readr::read_csv(normalizePath(paste0("~/", output_path))))
